---
title: "NLP with Shrek Script"
author: "Your Name"
date: "`r Sys.Date()`"
output: html_document
---

```
```{r}
install.packages("tidytext")
install.packages("dplyr")
install.packages("stringr")
install.packages("ggplot2")
install.packages("wordcloud")
install.packages("tm")
install.packages("sentimentr")
install.packages("knitr")
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
This R Markdown document demonstrates Natural Language Processing (NLP) techniques using the a movie script of your choosing.

## Load Libraries
```{r}
library(tidytext)
library(dplyr)
library(stringr)
library(ggplot2)
library(wordcloud)
library(tm)
library(sentimentr)
```

## Load and Preprocess Script
```{r}
# Load script from URL - find your own on imsdb.com
url <- "https://imsdb.com/scripts/Shrek.html"

script_text <- readLines(url, warn = FALSE)

# Extract main content (remove HTML tags)
script_text <- script_text %>% paste(collapse = " ") %>% str_replace_all("<.*?>", " ")

# Convert to tibble
data <- tibble(text = unlist(str_split(script_text, "\n")))
```

## Tokenization and Word Frequency
```{r}
tokens <- data %>%
  unnest_tokens(word, text) %>%
  anti_join(stop_words, by = "word")

word_counts <- tokens %>%
  count(word, sort = TRUE)

# Plot top words
word_counts %>%
  top_n(20) %>%
  ggplot(aes(x = reorder(word, n), y = n)) +
  geom_col(fill = "blue") +
  coord_flip() +
  labs(title = "Top Words in Shrek Script", x = "Word", y = "Count")
```

## Word Cloud
```{r}
wordcloud(words = word_counts$word, freq = word_counts$n, min.freq = 10, colors = brewer.pal(8, "Dark2"))
```

## Sentiment Analysis
## Details on sentimentr polarity score https://rdrr.io/cran/sentimentr/man/sentiment.html
```{r}
sentiment_scores <- sentiment(data$text)

ggplot(sentiment_scores, aes(x = sentiment)) +
  geom_histogram(binwidth = 0.1, fill = "red", color = "black") +
  labs(title = "Sentiment Distribution in Shrek Script", x = "Sentiment Score", y = "Frequency")
```

## Analyzing the sentiment over the course of the movie.

```{r}

plot(x = sentiment_scores$sentence_id,
     y = sentiment_scores$sentiment,
     xlab = "Sentence no.",
     ylab = "Sentiment score",
     main = "Sentiment development over sentences",
     type = "l",
     bty = "n")
```


## Conclusion
This the end of a basic NLP technique walkthrough including text preprocessing, word frequency analysis, and sentiment analysis using a movie script.
